%-------------------------
% Resume in LateX
% Author : Ilia Boiko, the original template is taken from https://www.overleaf.com/latex/templates/dphang-cv-template/wygbzfpbdhnj, but changed A LOT in the process.
% License : MIT
%------------------------

\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{fontawesome5} % Include fontawesome5 here
\usepackage{enumitem}
\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
{<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{#1}}%
     \item[]
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{-0.5#1}}%
\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 &
#2 \\
\end{tabular*}}


% and the actual content starts here
\begin{document}

\begin{center}
	{\LARGE \textbf{Ilia Boiko}}
	\\ Tbilisi, Georgia
	\vspace{0.05cm}
	\\
	\raisebox{-0.2\height}{\Large \faEnvelopeSquare} boikoilia.career@gmail.com \hfill \raisebox{-0.2\height}{\Large \faLinkedin} https://www.linkedin.com/in/ilia-boiko-93449112b \hfill \raisebox{-0.2\height}{\Large \faGithubSquare} github.com/furagi \hfill 
\end{center}

%====================================== Summary ======================================
\subsection*{\Large Senior Full-Stack Software Engineering Team Lead}
\vspace{-.5em}
\hrule
\vspace{1em}
Results-driven software engineering team lead with 10+ years of experience in designing, building and scaling software products. Proven track record in leading high-performing teams, re-architecting systems to enhance product stability and security. Expertise in full-stack development with modern technologies including Python, Django, FastAPI, TypeScript, React, NestJS, PostgreSQL, MongoDB, AWS and GraphQL. Passionate about domain-driven design (DDD), distributed systems and fostering strong development cultures through Agile/Scrum methodologies.

%====================================== Skills ======================================
\subsection*{\Large Skills}
\vspace{-.5em}
\hrule
\vspace{1em}
\begin{itemize*}
	\item {\textbf{Software Development:}} Python, Django, FastAPI, TypeScript, React, Redux, Next.js, NestJS, Apollo GraphQL,  Node.js, Jest, React Testing Library.
	\item {\textbf{Databases \& Cloud:}} PostgreSQL, MongoDB, RabbitMQ, Prisma, Redis, AWS, GCP.
	\item {\textbf{DevOps \& Tools:}} Nx, Docker, CI/CD, Git, Github Actions.
	\item {\textbf{Development Practices:}} Agile/Scrum, TDD, System Design, Microservices Architecture, Domain-Driven Design (DDD).
	\item {\textbf{Languages:}} Fluent in Russian and English.
\end{itemize*}

%====================================== Recent Experience ======================================

\subsection*{\Large Professional Experience}
\vspace{-.5em}
\hrule
\vspace{1em}
\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
	\item
		\headerrow
		{\textbf{Bazaar Origin}}
		{\textbf{Remote}}
		\headerrow
		{\emph{Software Engineering Team Lead}}
		{\emph{October 2023 -- Present}}
		\begin{itemize*}
			\item Led a full-scale project reboot, transforming a struggling startup into a stable, scalable product.
			\item Built and managed a high-performing 11-member cross-functional team (frontend, backend, QA and design), fostering cross-functional collaboration and improving development and release workflows to enhance product quality.
			\item Established Agile/Scrum practices and implemented and set up CI/CD pipelines, improving team performance by 20\%.
			\item Re-architected system components to address security and performance bottlenecks, boosting system performance by 60\% (component-dependent) and reducing technical debt by 80\%.
			\item Designed and implemented critical frontend and backend components, ensuring scalability and maintainability.
			\item Led the development of a Telegram spam prevention bot, reducing moderation team efforts by 90\%.
		\end{itemize*}
		\vspace{-1em}
		\begin{flushleft}
			{\textbf{Tech stack:}} Python, Django, PostgreSQL, MongoDB, Docker, RabbitMQ, TypeScript, NestJS, AWS, Next.js, React, Jest, React Testing Library, and Apollo GraphQL.
		\end{flushleft}
	\item
		\headerrow
		{\textbf{SupportLogic.com}}
		{\textbf{Remote}}
		\headerrow
		{\emph{Senior Full Stack Engineer}}
		{\emph{April 2022 -- October 2023}}
		\begin{itemize*}
			\item Developed a new email support app, expanding company's core product capabilities.
			\item Improved and maintained the company's component library, optimizing usage patterns in a core product. Introduced TDD and enhanced linting configurations, led improving of TypeScript interfaces, thus reducing code review time by 30\%.
			\item Led the development of a local dev environment project, reducing developer onboarding time by 40\%.
			\item Architected and led development of an automated customer onboarding product, accelerating the onboarding process by 90\%.
			\item Resolved tech debt in a newly acquired product, improving both frontend and backend by refactoring raw SQL-heavy code and fixing architectural issues.
		\end{itemize*}
		\vspace{-1em}
		\begin{flushleft}
			{\textbf{Tech stack:}} TypeScript, React, Jest, React Testing Library, Python, FastAPI, Django, PostgreSQL, Redis, Docker, GCP.
		\end{flushleft}
		\item
		\headerrow
		{\textbf{Genea}}
		{\textbf{Remote}}
		\headerrow
		{\emph{Senior Full Stack Engineer}}
		{\emph{September 2017 -- April 2022}}
		\begin{itemize*}
			\item Built a microservice to integrate 4 third-party camera providers, enabling future integrations with ease, and added live video support to the frontend application, contributing to securing deals with 3 new customers, including Shopify.  
			\item Improved the frontend application code structure and Webpack configuration, reducing the build time by 60\%, the bundle size over 2x, the codebase size by 15\%, and the app loading time by 40\% for new visitors and over 6x for returning ones.
			\item Raised the frontend application's unit test coverage from 0\% to 80\%, thus reducing bugs by 20\% on average.
			\item Completely revamped the frontend application design (at the CEO's request), significantly reducing the technical debt in the process.
		\end{itemize*}
		\vspace{-1em}
		\begin{flushleft}
			{\textbf{Tech stack:}} TypeScript, React, Redux, Jest, Python, FastAPI, NestJS, PostgreSQL, RabbitMQ, Docker, Heroku.
		\end{flushleft}
\end{itemize}

% restore the default list behavior
\renewcommand\labelitemi{$\bullet$}

%====================================== Other Experience ======================================

\subsection*{\Large Additional Experience}
\vspace{-.5em}
\hrule
\vspace{1em}
\begin{itemize*}
	\item \textbf{mySocial, Senior Full Stack Engineer:} React, Redux, TypeScript, Firebase, Google Cloud Functions.
	\item \textbf{Soshace.com, Middle/Senior FullStack Developer:} MongoDB, AngularJS, ExpressJS.
	\item \textbf{GTFlix TV/Avodn: Junior/Middle JS Developer:} MongoDB, ExpressJS, BackboneJS, MySQL, Ruby-on-Rails.
\end{itemize*}

%====================================== Education ======================================
\subsection*{\Large Education}
\vspace{-.5em}
\hrule
\vspace{1em}

\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
	\item
	      \headerrow
	      {\textbf{KnASTU}}
	      {\textbf{Komsomolsk-on-Amur, Russia}}
	      \headerrow
	      {\emph{B.S. Mathematics and Computer Science} (\textbf{GPA:} 4.4/5)}
	      {\emph{September 2008 -- June 2012}}
	      	      
\end{itemize}

\end{document}